\documentclass{article}
\thispagestyle{plain}
\linespread{1.5}
\begin{document}
\begin{center}
{\bfseries \LARGE 10 odd factors that affect your mood}
\end{center}
\begin{center}
Fangfang Li
\end{center}
\begin{center}
\today
\end{center}
\par The color red can make someone more attracted to you. After reading this article, I finally understand the reason why people wear red when they get married. Color can affect your mood in many different ways, but its effects are largely dependent on your culture. Eating fish can help fight depression. Aside from looking pretty, fish actually can make you happier. I want to know whether the person who likes fish is very beautiful. I don't like fish so I'm not pretty. Wine can make you happier.I don't understand the question. Doesn't drinking make people sad? But red wine is out of the list. It has been known that red wine is capable of curing stomach ills, fighting aging, and much more. It long been an accepted fact that music can influence the human mind; however, researchers from the University of Groningen have found that music can actually change the way you perceive another person. I agree with that. If you e in a crowd of people and you hear a happy song, you  more likely to recognize the happy expressions in the crowd rather than the sad ones. The opposite applies to sad songs.Love can make you a jerk. Men with girlfriends, were more likely to be aggressive or even harmful to members of the same sex. Your facebook friends can put you in a bad mood.For example,A study conducted by German scientists shows that pictures of trips to distant lands or of new, expensive purchases your friends have made, can make you less excited about the things in your own life.
\par Finally,your night light can make you depressed. It may have something to do with the fear of loneliness. I think people's life is very short, people should be happy every day.
\footnote{from"China Daily"}
\begin{thebibliography}{99}
\bibitem{pa} Jane Raymond.~
Emotion in Spreaking and Singing~[J].~SJGT Thieme.~2004~(03):~146~-~149.

\end{thebibliography}
\end{document}
