\documentclass{article}
\usepackage{ctex}
\usepackage{multicol}
\usepackage[top=1in, bottom=1in, left=1.25in, right=1.25in]{geometry}
\usepackage{lscape}
\author{Fangfang Li}
\date{April 17, 2018}
\title{Why sitting at your desk may make you STUPID}
\begin{document}
\maketitle
Today I read an article regarding why sitting at your desk may make you STUPID. Sitting at your desk all day or on your sofa watching TV could make you stupid, scientists have suggested.

If you are a student or have to sit down to work, you should stand up and exercise for a while. Don't let yourself stay sedentary. Sitting for long periods of time can be harmful to one's health. I feel this is a common sense. I believe most people know that exercise makes people healthy. Researchers have discovered those with a sedentary lifestyle have a smaller brain region important in forming memories. No further explanation was given for the area of memory. I think it means memory loss. The study adds to a growing list about the dangers of sitting for too long.                The new research suggests sitting for too long could even boost the risk of dementia. The article also mentions a number of technical terms to explain the harmful effects of sitting, for example, hippocampus, the left temporal lobe and the right temporal lobe.

I think proper exercise can eliminate this disadvantage. After studying and working for a while, take a break for about ten minutes. For certain work, sitting is inevitable, but I think the harm is not terrible. you should learn to work with happy.

\end{document}
