\documentclass{article}

\usepackage{ctex}

\usepackage{multicol}

\usepackage[top=1in, bottom=1in, left=1.25in, right=1.25in]{geometry}

\usepackage{lscape}

\author{Fangfang Li}

\date{April 9,2018}

\title{study: Being forgetful might actually mean you're smarter}


\begin{document}


\maketitle


Recently,I read an article about forgetfulness and memories. Recent research makes the case that being forgetful can be a strengt.In fact, selective memory can even be a sign of stronger intelligence. Good memories are very pround, but forgetfulness is not a shameful thing. Insteasd,the occasional lost detail can be a sign of a perfectly healthy memory system.The goal of memory is not the transmission of information through time.Rather, the goal of memory is to optimize decision-making. And making intelligent decisions does not mean you need to have all the information at hand, it just means you need to hold onto the most valuable information. Maybe remembering too many things is a stress on the brain .If you are trying to navigate the world and your brain is constantly bringing up multiple conflicting memories, that makes it harder for you to make an informed decision. Artcle author shows that to improve memory, we can try exercising like jogging, power walking, and swimming to increase the number of new neurons in our brain¡¯s learning region.


By reading this article£¬ I understand a truth that our brains are working smarter when they aim to remember the right stories, not every story.This is the first time I write article in English,I will read more English to improve my English.


\end{document}
